### 2015-11-26 Irregular-occ/Irregular-occ.tex
.

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0.% For Themisto's case, the small number of observations meant that the statistical uncertainty was even greater than the obtained elements, though the fitting proved satisfying. We decided to provide its elements with significant number comparable to the other satellite for information, but left it without uncertainty.
 }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & I$\degr$ (EQJ2000) & $\Omega\degr$ & $\omega\degr$ & $v$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular}

\end{center}
\end{table*}

@@

In this work, the STE was used in all but three satellites, not Jovian ones. For these 3 cases, the JPL ephemeris was used instead. The JPL ephemeris for Phoebe is of enough high quality for the short term, mostly thanks to the observations by Cassini \textcolor{red}{(é verdade? O paper do Tadjedine foi usado pelo JPL? dar alguma citacao aqui)}. In the case of Triton, the JPL ephemeris is also good enough, as the relatively large diameter of Triton favours the positive detection of occultations. A new short term ephemeris for Nereid is however still needed, but its production was beyond the scope of this work, so we used the JPL ephemeris in this case too.

@@

>>>>

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0.% For Themisto's case, the small number of observations meant that the statistical uncertainty was even greater than the obtained elements, though the fitting proved satisfying. We decided to provide its elements with significant number comparable to the other satellite for information, but left it without uncertainty.
 }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & I$\degr$ & $\Omega\degr$ & $\omega\degr$ & $v\degr$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular} 
\end{center}
\textbf{Notes}: a: Semimajor axis; e : Excentricity; I: Inclination relative to the Equatorial Reference Plane J2000; $\Omega$: Longitude of the ascending node; $\omega$: Argument of periapsis; $v$: True Anomaly.
\end{table*}

@@

In this work, the STE was used in all but three satellites, not Jovian ones. For these 3 cases, the JPL ephemeris was used instead. The JPL ephemeris for Phoebe is of enough high quality for the short term, mostly thanks to the observations by Cassini. In the case of Triton, the JPL ephemeris is also good enough, as the relatively large diameter of Triton favours the positive detection of occultations. A new short term ephemeris for Nereid is however still needed, but its production was beyond the scope of this work, so we used the JPL ephemeris in this case too.

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=17.6cm]{figures/HIMALIA.eps}
\caption{TESTE DE MAPA. STE = AZUL, JPL=VERMELHO, 22FEV=PRETO, 03MAR=VERDE%Predictions for Himalia: The straight lines show the size of the shadow. The big red dot show the geocentric closest approach of the shadow. The black "+" marks at maps (b,c,d) are the STE prediction closest approach for reference. The small red ones are the center of the shadow separated by one minute. \ref{Fig: occ-Himalia-STE} is the map using the STE ephemeris showed in Sec. \ref{Sec: integration}. \ref{Fig: occ-Himalia-JPL} shows the shadow using the JPL ephemeris. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. The green dot at the bottom of the maps is the location of Observatório do Pico dos Dias.
}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}
